\chapter{Game Overview}\label{ch:overview}

\section{Concept}

The game follows the story of a train that travels through the frozen wasteland that makes up the Earth of the not-so-distant future.
As far as the player and all characters are convinced, the train is the last bastion of humanity.
The train is powered by a fusion engine that collects hydrogen from the snow, which requires it to keep moving.
As such, the player needs to ensure the train does not stop due to lack of power or mechanical failure.
Through careful management of resources, the player can ensure the train keeps running and the last humans on the train survive.

\section{Genre}

The game is a real-time strategy game focused on resource management.
It is important to balance the resources of the train to keep it running and the people happy.

\section{Target Audience}

The game is targeted at players who enjoy strategy games and resource management.
The gameplay is rarely action-oriented, and the player has plenty of time to make decisions.
The game is also targeted at players who enjoy a good story, which can be influenced by the player's decisions.
Since the themes are often quite dark, the game is primarily targeted at adults.

\section{Gameplay Highlights}

The game will feature a story that is influenced by the player's decisions.
Many random and scripted events will occur to ensure a thrilling experience and some degree of replayability.
Resource management needs to be balanced carefully, because margins for error are often small.

\section{Technology Highlights}

Using the Unreal Engine 5, the game will feature high-quality graphics and audio.
Thanks to latest advances like Nanite or Volumetric Clouds, stunning visuals will be possible on the outside of the train, which is the primary view of the game.
To get an idea of the current location and progress of the train along the globe-spanning track, it will be possible to view a map of the entire world.
The transition between the two views will be seamless, and the player can zoom in and out of the map to get a better view of the train's surroundings.

\section{Art and Audio Highlights}

The game will feature a realistic art style, with a focus on the train and its surroundings.
The train will be moderately detailed to allow for an interesting view from the outside.
The game will feature a dynamic soundtrack that changes depending on the current situation.
The soundtrack will be mostly orchestral and consist of royalty-free music.

\section{Hardware Requirements}

The game will require a modern PC with a dedicated graphics card.
