\chapter{Game World}\label{ch:game-world}

\section{Overview}

The game plays in the remains of Earth in the year 2115.
After a terraforming experiment intended to reverse climate change, the Earth froze over.
All plants, animals, and people who did not find shelter in the few weeks after the Great Freeze, died.
Only a single train, built by a visionary inventor who questioned the terraforming experiment, survived and kept running.
Those who made it onto the train, with a ticket or not, survived until today.
For these people, the train is all that is left of the world, apart from the stunning view of the frozen wasteland outside.

\section{Backstory}

The runaway greenhouse effect caused by climate change was a major threat to humanity.
To counteract this, a group of scientists developed a terraforming experiment that would reverse the effects of climate change.
Using an atmospheric agent that would reflect sunlight, the scientists hoped to cool down the Earth and reverse the greenhouse effect.
However, the experiment went wrong due to miscalcuations of the autoreactive properties of the agent.
Instead of cooling down the Earth, the agent caused a runaway cooling effect, freezing the entire planet.

The scientists who developed the experiment were among the first to die, and the rest of humanity was not prepared for the sudden change.
Only a few people managed to find shelter in the few weeks after the Great Freeze:
Underground bunkers, nuclear reactors, submarines -- they all failed to keep their inhabitants alive due to immobility or lack of resources.

Only a single train, built by a visionary inventor who questioned the terraforming experiment from the beginning, survived and kept running.
Shortly after it's announcement, the train was ridiculed by the media and the public to be a cash grab and hopeless endeavor.
However, the inventor managed to convince a few people to invest in the train, and it was built in secret.
Those investors, alogn with their families, were the first to board the train with tickets.
In addition, hundreds of people were hired to keep the train running, and they were allowed to bring their families along.
As the temperatures dropped, many more streamed to the station, hoping to find shelter on the train.
The inventor ordered his security personell to keep them off the train, leaving them to die in the cold, but some managed to sneak or fight their way on board.

It is now that the player assumes control of the train, and the fate of the last humans on Earth is in their hands.

\section{Locations}

The game features a single train that travels along a track that spans the entire globe.
Few locations are still recognizable, let alone useful, but some are still worth stopping at.

\subsection{Departure Station}

The departure station is the place where the train started its journey.
It is located in the middle of a large city, which is now covered in snow and ice.
The station is mostly intact, but the city is destroyed.
Apart from the memories and bodies left behind, there is nothing of value to be found here.

\subsection{Junction}

A junction is place where the player can choose which path to take.
The train can only travel along one path, and the other path will can be taken on the next rotation, as long as the track leads back to the main track.
Choosing a different path may lead to new locations, events and resources, but it may also lead to a dead end or other dangers.

\subsection{Broken Tracks}

Some sections of the track may be in bad condition.
The player can choose to stop and repair the tracks, which will cost time and resources, but will allow the train to pass through the section without problems on future rotations.
Alternatively, the player needs to slow down to prevent the loss of wagons or event a derailment, which will end the game.

\subsection{Research Station}

The research station is a place where scientists worked on the terraforming experiment.
It can be manned to investigate new insights about the experiment, which may lead to new events and resources.

\subsection{Depots}

Depots are places where resources can be gathered.
They are often in remote places, and stopping will be dangerous for the train and the people who leave it.
Once plundered, a depot will be empty and useless.

\section{Resources}

There are a number of resources that need to be managed to keep the train running.

\subsection{Power}

The train is powered by a fusion engine that collects hydrogen from the snow.
The engine feeds power into a number of battery cars, which store the power for later use.
Stopping or slowing the train will reduce the amount of power generated, and the train will eventually run out of stored power.
The amount of power usage depends on the interior temperature of the train, which can be lowered to reduce power usage, but make the people unhappy.
In some parts of the track, more power may be needed to climb mountains, while in other parts, the train may be able to coast downhill.

\subsection{Temperature}

The main function of the train is to keep the people on board warm.
The temperature inside the train can be adjusted individually for each wagon, but the people will be unhappy if it is too cold.
Some wagons might be destroyed completely if the temperature drops to low, e.g. the greenhouse, slaughterhouse or aquarium.
Mechanical failures may also lower the temperature if the wagons are not repaired in time.

\subsection{Food}

The train needs to be stocked with food to keep the people alive.
The food is produced in greenhouse, slaughterhouse and fishery wagons.
The food can be distributed to the people, but they will be unhappy if they do not get enough.
The food can also be used to feed animals, which will produce other resources like Honey or Meat in return.
This may make certain groups of people happier, but others may be unhappy about the animals on the train.

\subsection{Freshwater}

The people on the train need water to drink and wash themselves.
The water is recycled in the water treatment wagon, and can be distributed to the people.
This is a secondary resource, as it will be generally available as long as the water treatment wagon is working and no pipes are broken.

\subsection{People}

The people on the train are the most important resource.
They keep the train running, and they need to be kept happy to avoid a mutiny.
The people can be assigned to different jobs depending on their age and skills, and they will be unhappy if they are not assigned to a job.
Depending on the job, they can inhabit different quality wagons ("classes") and have different needs.
For example, a worker needs only basic resources, while a scientist has higher needs, and an investor wants to live in luxury.

\section{Characters}

Multiple advisors will help the player to make informed decisions.
There is an advisor for every important resource and aspect of the train.
The advice can be followed or ignored, but ignoring it too often will lead to a disgruntled advisor or event mutiny.
The following jobs, and subsequently advisors, are available:

\subsection{Investor}

Investors do not work, but they inhabit a first class wagon.
They are the most important people on the train, and they will be unhappy if they do not get what they want.

\subsection{Engineer / Head of Engineering}

The engineer is responsible for the power supply of the train.
Engineer is a second class job, while the Head of Engineering is a first class job.

\subsection{Scientist / Head of Research}

Scientists can be sent to a research station or work on the train.
They have a second class job, while the Head of Research has a first class job.
Scientists can be doctors, engineers, or other specialists.
Doctors can be sent to the hospital to heal people, while engineers can be sent to repair broken wagons.

\subsection{Farmer / Head of Agriculture}

The farmer works in the greenhouse and slaughterhouse, producing food.
Farming is a third class job and the Head of Agriculture is a second class job.

\subsection{Fisherman/Slaughterman / Head Chef}

The fisherman works in the fishery, producing fish for first class people, while themselves having a second class job.
The slaughterman works in the slaughterhouse, producing meat for second class people, while being a third class job.
The Head Chef works in the kitchen, producing food for first class people, while being a second class job.

\subsection{Security Guard / Head of Security}

Security guards are responsible for keeping the people on the train in check.
They have a third class job, while the Head of Security has a second class job.

\subsection{Worker / Facility Manager}

Workers work in the engine room, water treatment wagon, and other places.
They have a third class job, and they are the most common people on the train.
The Facility Manager is a second class job, and they are responsible for the general maintenance of the train.

\section{Missions}
